---
title: "Analysis of Sales Report of a Clothes Manufacturing Outlet"
author: "Andrei Enescu"
date: "10/12/2020"
output:
  pdf_document: default
---

# Background and Objective
A high-end fashion retail store is looking to expand its products. 
It wants to understand the market and find the current trends in the industry. 
It has a database of all products with attributes, such as, style, material, 
season, and the sales of the products over a period of two months. 

# Domain: 
Retail

# Dataset Description:
There are two files provided: Atribute DataSet.xlsx and Dress Sales.xlsx


# Analysis Tasks: 
There are 5 goals / questions for this project  
1. To automate the process of recommendations, the store needs to analyze the 
given attributes of the product, like the style, season, etc., and come up with
a model to predict the recommendation of products (in binary output – 0 or 1) 
accordingly.  
2. In order to stock the inventory, the store wants to analyze the sales data
and predict the trend of total sales for each dress for an extended period of
three more alternative days.  
3. To decide the pricing for various upcoming clothes, they wish to find how
the style, season, and material affect the sales of a dress and if the style of
the dress is more influential than its price.  
4. Also, to increase sales, the management wants to analyze the attributes of
dresses and find which are the leading factors affecting the sale of a dress.  
5. To regularize the rating procedure and find its efficiency, the store wants
to find if the rating of the dress affects the total sales  


*****
These are the packages / libraries used
```{r Packages and libraries, warning=FALSE,message=FALSE}
library(plyr)
library(dplyr)
library(rio)
library(raster)
library(data.table)
library(lattice)
library(ggplot2)
library(caret)
library(caTools)
library(forecast)
library(corrplot)
```

First, I imported the two datasets:       
1. Attribute DataSet.xlsx contains all the attributes of the dresses and also a 
recomandation column (binary value suggesting a recommendation (1) or not (0))  
2. Dress Sales.xlsx contains the sales for each dress on a particular date.
Date ranges from 29/8/2013 to 12/10/2013, and the sales are registered for
alternative days.

```{r}
Attrset <- import("Attribute DataSet.xlsx")
Sales.dates <- import("Dress Sales.xlsx")

View(Attrset)
str(Attrset)
```

## **Data Preparation**

### Converting from Character to Factor

```{r}
Attrset <- mutate_if(Attrset, is.character, as.factor)
```

### Renaming the factor levels as there were misstypes in the original dataset

```{r}
levels(Attrset$Style)
Attrset$Style <-  revalue(Attrset$Style, c("sexy" = "Sexy"))

levels(Attrset$Price)
Attrset$Price <- revalue(Attrset$Price, c("high" = "High"))
Attrset$Price <- revalue(Attrset$Price, c("low" = "Low"))

levels(Attrset$Size)
Attrset$Size <- revalue(Attrset$Size, c("s" = "S"))
Attrset$Size <- revalue(Attrset$Size, c("small" = "S"))

levels(Attrset$Season)
Attrset$Season <- revalue(Attrset$Season, c("Automn" = "Autumn"))
Attrset$Season <- revalue(Attrset$Season, c("spring" = "Spring"))
Attrset$Season <- revalue(Attrset$Season, c("summer" = "Summer"))
Attrset$Season <- revalue(Attrset$Season, c("winter" = "Winter"))

levels(Attrset$NeckLine)
Attrset$NeckLine <-
  revalue(Attrset$NeckLine, c("sweetheart" = "Sweetheart"))

levels(Attrset$SleeveLength)
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("cap-sleeves" = "capsleeves"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("half" = "halfsleeve"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("sleeevless" = "sleeveless"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("sleevless" = "sleeveless"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("sleveless" = "sleeveless"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("threequater" = "threequarter"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("thressqatar" = "threequarter"))
Attrset$SleeveLength <- revalue(Attrset$SleeveLength,
                                c("urndowncollor" = "turndowncollor"))

levels(Attrset$Material)
Attrset$Material <- revalue(Attrset$Material, c("model" = "modal"))

levels(Attrset$FabricType)
Attrset$FabricType <-
  revalue(Attrset$FabricType, c("shiffon" = "chiffon"))
Attrset$FabricType <-
  revalue(Attrset$FabricType, c("flannael" = "flannel"))
Attrset$FabricType <-
  revalue(Attrset$FabricType, c("knitting" = "knitted"))
Attrset$FabricType <-
  revalue(Attrset$FabricType, c("sattin" = "satin"))
Attrset$FabricType <-
  revalue(Attrset$FabricType, c("wollen" = "woolen"))

levels(Attrset$Decoration)
Attrset$Decoration <-
  revalue(Attrset$Decoration, c("none" = "null"))

levels(Attrset$`Pattern Type`)
Attrset$`Pattern Type` <- revalue(Attrset$`Pattern Type`,
                                  c("leapord" = "leopard"))
Attrset$`Pattern Type` <- revalue(Attrset$`Pattern Type`,
                                  c("none" = "null"))
```


Second dataset - data preparation
```{r}
View(Sales.dates)

setnames(
  Sales.dates,
  old = c(
    "41314",
    "41373",
    "41434",
    "41495",
    "41556",
    "41617",
    "41315",
    "41374",
    "41435",
    "40400",
    "41557",
    "41618"
  ),
  new = c(
    "2/9/2013",
    "4/9/2013",
    "6/9/2013",
    "8/9/2013",
    "10/9/2013",
    "12/9/2013",
    "2/10/2013",
    "4/10/2013",
    "6/10/2013",
    "8/10/2013",
    "10/10/2013",
    "12/10/2013"
  )
)
```

Replacing the NA values with the mean of the row and also replacing some
character values with NA.  
After Rowmean was calculated I formatted the data frame to have the values
without decimals

```{r, warning=FALSE}
sapply(Sales.dates, class)

Sales.dates[Sales.dates == "removed"] <- NA
Sales.dates[Sales.dates == "Removed"] <- NA
Sales.dates[Sales.dates == "Orders"] <- NA

Sales.dates[9:14] <-
  mutate_if(Sales.dates[9:14], is.character , as.numeric)

Sales.dates <-
  (is.na(Sales.dates)) * rowMeans(Sales.dates[2:24], na.rm = T)[row(Sales.dates)] +
  replace(Sales.dates, is.na(Sales.dates), 0)

Sales.dates <-
  Sales.dates %>% mutate_at(vars(-Dress_ID), funs(round(., 0)))
```

Calculating the Total sales from the Sales.dates data frame (both row and 
column wise); this will be used later in the analysis
```{r}
Totalsales <- rowSums(Sales.dates[2:24])
TotalSalescol <- colSums(Sales.dates[2:24])
Sales.dates <- data.frame(Sales.dates, Totalsales)
```

Merging the two data frames; this will be used later in the analysis

```{r}
TotalDF <- merge(Attrset, Sales.dates)
```

*****
# **Question 1**
To automate the process of recommendations, the store needs to analyze the 
given attributes of the product, like the style, season, etc., and come up with
a model to predict the recommendation of products (in binary output – 0 or 1)
accordingly.   

Bellow I use a logistic regression model. For this the variables are:   
1. Dependent variable: Recommendation  
2. Remaining variables, except Dress_ID, which is an identifier   

For this model I am creating a new data frame without the Dress_ID and NA rows

```{r}
Attrib <- Attrset[, -1]
Attrib <- na.omit(Attrib)

fit1 <-
  glm(
    Recommendation ~ Style + Price + Rating + Size + Season +
      NeckLine + SleeveLength + waiseline + Material + FabricType +
      Decoration + `Pattern Type`,
    family = binomial(),
    Attrib
  )
summary(fit1)
```


## Observations related to Question 1

In the above model we can see that **Price, Season** and **Rating** are the main 
attributes of the dress that are affecting the recommendation.  
Furthermore the Residual deviance is lower than the Null deviance, this means
that using this model for prediction will be close to the actual values of
recommendation.


I am also testing and validating the model. 
Splitting the data into 80% Training and 20% Testing

```{r}
set.seed(1)
inTrain <-
  createDataPartition(Attrib$Recommendation, p = 0.8, list = FALSE)
Training <- Attrib[inTrain, ]
Testing <- Attrib[-inTrain, ]

fit2 <-
  glm(
    Recommendation ~ Style + Price + Rating + Size + Season + NeckLine +
      SleeveLength + waiseline + Material + FabricType + Decoration +
      `Pattern Type`,
    family = binomial(),
    Training
  )
summary(fit2)
```

Creating a new column for prediction of recommendation
```{r}
Testing$Predict.recommend <- 0
```

There were some errors after the split, because some levels of the attributes
had values only in the Testing set. The values are small and the impact
on predication is insignificant so I decided to have the same values for the bellow
levels in both, Training and in Testing data sets

```{r}
fit2$xlevels[["Style"]] <-
  union(fit2$xlevels[["Style"]], levels(Testing[["Style"]]))
fit2$xlevels[["NeckLine"]] <-
  union(fit2$xlevels[["NeckLine"]], levels(Testing[["NeckLine"]]))
fit2$xlevels[["Decoration"]] <-
  union(fit2$xlevels[["Decoration"]], levels(Testing[["Decoration"]]))
fit2$xlevels[["Pattern Type"]] <-
  union(fit2$xlevels[["Pattern Type"]], levels(Testing[["Pattern Type"]]))

Pred <- predict(fit2, Testing, type = "response")
```

Setting threshold as 0.7 for the probability
```{r}
Testing$Predict.recommend <- ifelse(Pred >= 0.7, 1, 0)
Testing$Predict.recommend
```

Testing by confusion matrix
```{r}
table(Testing$Recommendation,
      Testing$Predict.recommend,
      dnn = list("Actual", "Predicted"))

conf.matrix <-
  table(Testing$Recommendation, Testing$Predict.recommend)
```

Accuracy and error of the model: 
```{r}
sum(conf.matrix)
sum(diag(conf.matrix)) / sum(conf.matrix)

1 - sum(diag(conf.matrix)) / sum(conf.matrix)
```

## Overall observation  

The accuracy of the test model is only 53.54%

*****
# **Question 2**
In order to stock the inventory, the store wants to analyze the sales data and
predict the trend of total sales for each dress for an extended period of three
more alternative days.

In order to predict the trend of total sales for an extended period of three
more days I used the *auto.arima* function.  
In this part of the analysis I am using the *TotalSalescol* created in the
Data Preparation part.

```{r}
is.vector(TotalSalescol)
TotalSalescol
Trend.Pred <- ts(TotalSalescol, start = 1, frequency = 7)
summary(Trend.Pred)

Trend.Pred <- auto.arima(Trend.Pred)
summary(Trend.Pred)

forecast(Trend.Pred, 3)
plot(forecast(Trend.Pred, 3))
```
## Observation  

As we can see from the plot and the ARIMA model output, there is a high 
fluctuation in the confidence interval

*****
# **Question 3**
To decide the pricing for various upcoming clothes, they wish to find how the 
style, season, and material affect the sales of a dress and if the style of the
dress is more influential than its price.

In this part of the analysis I am using the *TotalSales* created in the
Data Preparation part.  
Also I am using the ANOVA model to find the effect of **Style, Season** and
**Material** on Total Sales.  
After ANOVA I am using the linear regression model in order to find the
relation of the three attributes on Total Sales and then just for the **Price** 
and **Styele**

```{r}
ANOVA.Style <- aov(TotalDF$Totalsales ~ TotalDF$Style)
ANOVA.Season <- aov(TotalDF$Totalsales ~ TotalDF$Season)
ANOVA.Material <- aov(TotalDF$Totalsales ~ TotalDF$Material)
summary(ANOVA.Style)
summary(ANOVA.Season)
summary(ANOVA.Material)

fit3 <- lm(Totalsales ~ Style + Season + Material, TotalDF)
summary(fit3)

fit4 <- lm(Totalsales ~ Price + Style, TotalDF)
summary(fit4)
```

## Observation  

By using the ANOVA model individually on the three attributes we can conclude
that Style has the lowest p value (0.135) among the three attributes so it has
the most impact in the Total Sales.
In the linear regression model *fit3* we can see that the Style Sexy is 
affecting (in a low manner) the Total Sales.
Also for model *fit4*, the Style has a higher impact then the price in the
Total Sales of the dress.
However both models have a low R and R adjusted values, which means that the
models using only these attributes can't be used in predicting the Total Sales.

*****
# **Question 4**
Also, to increase sales, the management wants to analyze the attributes of 
dresses and find which are the leading factors affecting the sale of a dress.

I am creating a new linear regression models with TotalSales as a dependent
variable and the rest (except Dress_ID) as independent variable.


```{r}
TotalData <- TotalDF[,-c(1, 15:37)]
fit5 <- lm(Totalsales ~ ., TotalData)
summary(fit5)
```

## Observation 

We can see in the output of the model that we have a lot of variables affecting
the Total Sales. We can split the variables in high and moderate impact
and also positive and negative impact.

1. High - positive impact variables
  a) Rating
  b) Size L
  c) NeckLine ruffled
2. Moderate - positive impact variables
  a) Style Sexy
  b) Decoration Tiered
  c) Pattern Type geometric
3. Moderate - negative impact
  a) SleevLength
  
The multiple and adjusted R-squared values are 46% and 30% respectively. We 
can conclude that the model is quite fit and the p-value of almost 0 also 
suggests that there is definitely an impact of these variables on the total
sales of the dresses.

*****
# **Question 5**
To regularize the rating procedure and find its efficiency, the store wants to
find if the rating of the dress affects the total sales

In order to find if there is a relation between *Rating* and *Total Sales*,
I use *cor.test* function.

```{r}
corr <- cor.test(TotalDF$Totalsales, TotalDF$Rating)
corr
corr4plot <- cor(TotalDF[, c(4, 38)])
corrplot(corr4plot)
```

## Observation  

Based on the output of this function, we have a correlation of 0.2 between
the Total Sales and the Rating. This means that there is a weak - positive
correlation between the two attributes. In conclusion a higher rating will 
correlate with higher sales which suggests that the rating approach requires
regularization.

