---
title: "Web Data Analysis"
author: "Andrei Enescu"
date: "10/15/2020"
output: pdf_document
---

# Description
 
# Background and Objective:
   The web analytics team of www.datadb.com is interested to understand the 
 web activities of the site, which are the sources used to access the website. 
 They have a database that states the keywords of time in the page, source 
 group, bounces, exits, unique page views, and visits.

# Domain: Web

# Dataset Description:
   The variables in the dataset are defined here for better understanding:

# Analysis Tasks:
   The team is targeting the following issues:
   
 1. The team wants to analyze each variable of the data collected through data
 summarization to get a basic understanding of the dataset and to prepare for
 further analysis.

 2. As mentioned earlier, a unique page view represents the number of sessions
 during which that page was viewed one or more times. A visit counts all 
 instances, no matter how many times the same visitor may have been to your 
 site. So the team needs to know whether the unique page view value depends 
 on visits.

 3. Find out the probable factors from the dataset, which could affect the 
 exits. Exit Page Analysis is usually required to get an idea about why a user
 leaves the website for a session and moves on to another one. Please keep in 
 mind that exits should not be confused with bounces.

 4. Every site wants to increase the time on page for a visitor. This increases
 the chances of the visitor understanding the site content better and hence 
 there are more chances of a transaction taking place. Find the variables which
 possibly have an effect on the time on page.

 5. A high bounce rate is a cause of alarm for websites which depend on visitor
 engagement. Help the team in determining the factors that are impacting the
 bounce.

*****

Used libraries: 
```{r message=FALSE}
library(rio)
```

Importing the data using RIO library  
```{r}
webDF <- import("1555058318_internet_dataset.xlsx")
```

## 1. The team wants to analyze each variable of the data collected through data
## summarization to get a basic understanding of the dataset and to prepare for
## further analysis.

```{r}
View(webDF)
str(webDF)
webDF$Continent <- as.factor(webDF$Continent)
webDF$Sourcegroup <- as.factor(webDF$Sourcegroup)
summary(webDF)
```

### Observation

Based on the summary output we can conclude the following:  
 * Maximum Bounce is 30  
 * Maximum Exits is 36  
 * The website was visited mostly by visitors from *North America*  
 * Majority of the visits come from *Google*  
 * The average time spent on page was 73.18 seconds  
 

Summary grouped by Continent

```{r}
table(webDF$Continent)
by(webDF, webDF$Continent, summary)
```

### Observation

From the above data we can observe that:  
 * *North America* is the continent with the most bounces, most unique page views
 and most visits  
 * *SA* is the continent that has visitors with the most time spent on page.  
 * *AF* is the continent that has visitors with the least time spent on page.  

Summary grouped by Source group

```{r}
table(webDF$Sourcegroup)
by(webDF, webDF$Sourcegroup, summary)
```

### Observation  

From the above data we can observe that:  
 * *Google* source group has the most visitors and they spent the most time on 
 the website  
 * *(direct)* source group has the most unique page views, most exits and most
 bounces.  
 * *Facebook* source group has the least amount of visits and unique page views  

## 2. As mentioned earlier, a unique page view represents the number of sessions
## during which that page was viewed one or more times. A visit counts all 
## instances, no matter how many times the same visitor may have been to your 
## site. So the team needs to know whether the unique page view value depends 
## on visits.

**Option 1: ANOVA**
```{r}
UnqPg_View <- aov(Uniquepageviews ~ Visits, webDF)
summary(UnqPg_View)
```

**Option 2: Correlation function**
```{r}
cor(webDF$Uniquepageviews, webDF$Visits) 
```

### Observation  

Based on the ANOVA and correlation function output we can see that there is a 
strong positive relationship between the *unique page views* and the *visits*  

## 3. Find out the probable factors from the dataset, which could affect the 
## exits. Exit Page Analysis is usually required to get an idea about why a user
## leaves the website for a session and moves on to another one. Please keep in 
## mind that exits should not be confused with bounces.

```{r}
Ext <- aov(Exits ~ ., webDF)
summary(Ext)
```

### Observation  

From the above result of ANOVA we can observe that *Bounces*, *Continent*,
*Sourcegroup*, *Timeinpage* and *Uniquepageviews* have a higher significance 
over *Exits*. 
The *Exits* are less affected by *Visits*.  

## 4. Every site wants to increase the time on page for a visitor. This increases
## the chances of the visitor understanding the site content better and hence 
## there are more chances of a transaction taking place. Find the variables which
## possibly have an effect on the time on page.

```{r}
Time_Page <- aov(Timeinpage ~ ., webDF)
summary(Time_Page)
```

### Observation  

From the above result of ANOVA we can observe that *Bounces*, *Continent*,
*Sourcegroup*, *Uniquepageviews* and *Visits* have a higher significance 
over the time spent on page. 
The *Sourcegroup* doesn't have any impact on the time spent on page.    

## 5. A high bounce rate is a cause of alarm for websites which depend on visitor
## engagement. Help the team in determining the factors that are impacting the
## bounce.

```{r}
fit1 <- glm(
  BouncesNew ~ Timeinpage + Continent + Exits + Sourcegroup +
    Uniquepageviews + Visits,
  webDF,
  family = "binomial"
)
summary(fit1)
```

### Observation  

As it can be observed from the output shown above, the *Exits*, *Uniquepageviews*
and *Visits* are the variables that have the most impact on the bounce.