---
title: "Identifying and Recommending Best Restaurants"
author: "Andrei Enescu"
date: "11/13/2020"
output:
  pdf_document: default
---

# DESCRIPTION  

   A restaurant consolidator is looking to revamp the B2C portal using
 intelligent automation tech. This requires a different matrix to identify
 the star restaurants and generate recommendations. To make sure an effective
 model can be achieved, it is important to understand the behavior of the data
 in hand.  

   There are 2 datasets, data and Country-Code. Dataset data has 19 attributes
 and Country-Code has two attributes.  

   You are required to determine certain matrices to identify the star
 restaurants and generate recommendations.  

# Step to perform:  

# Importing, Understanding, and Inspecting Data :  

   Perform preliminary data inspection and report the findings as the structure
 of the data, missing values, duplicates, etc.  
   Based on the findings from the previous questions, identify duplicates and
 remove them  

# Performing EDA:  

1. Explore the geographical distribution of the restaurants and identify the 
cities with the maximum and minimum number of restaurants  
2. Restaurant franchising is a thriving venture. So, it is very important to 
explore the franchise with most national presence  
3. Find out the ratio between restaurants that allow table booking vs. those 
that do not allow table booking  
4. Find out the percentage of restaurants providing online delivery  
5. Calculate the difference in number of votes for the restaurants that deliver 
and the restaurants that do not deliver  
6. What are the top 10 cuisines served across cities?  
7. What is the maximum and minimum number of cuisines that a restaurant serves? 
Also, which is the most served cuisine across the restaurant for each city?
8. What is the distribution cost across the restaurants?  
9. How ratings are distributed among the various factors?  
10.Explain the factors in the data that may have an effect on ratings. 
For example, number of cuisines, cost, delivery option, etc.  

# Dashboarding:  

   Visualize the variables using Tableau to help user explore the data and 
create a better understanding of the restaurants to identify the ‘’star’’ 
restaurant  
   Demonstrate the variables associated with each other and factors to build a
dashboard  

*****

These are the libraries I used:  
```{r message=FALSE, warning=FALSE}
library(rio)
library(tmaptools)
library(plyr)
library(dplyr)
library(janitor)
library(ggplot2)
library(forcats)
library(plotly)
library(wordcloud)
library(tm)
library(tidyr)
library(stringr)
```

## Importing, Understanding, and Inspecting Data :

##   Perform preliminary data inspection and report the findings as the structure
## of the data, missing values, duplicates, etc.
##   Based on the findings from the previous questions, identify duplicates and
## remove them

```{r}
Cntry_code <- import("Country-Code.xlsx")
RestDF <- import("data.xlsx")

head(Cntry_code)
str(Cntry_code)
colnames(Cntry_code)
summary(Cntry_code)
which (is.na(Cntry_code))
sum(duplicated(Cntry_code))


head(RestDF)
str(RestDF)
colnames(RestDF)
summary(RestDF)
colnames(RestDF)[colSums(is.na(RestDF)) > 0]
which (is.na(RestDF$`Restaurant Name`))
which (is.na(RestDF$Cuisines))
```


There is one restaurant name missing and 9 records without cuisine.

Omitting the row without restaurant name and replacing the cuisine NA values
with "Other".

```{r}
RestDF$Cuisines[is.na(RestDF$Cuisines)] <- "Other"
RestDF <- na.omit(RestDF)


sum(duplicated(RestDF))
RestDF %>% get_dupes()
```

There are no duplicates  


Geocoding the missing locations  
```{r}
Rest_temp <- subset(RestDF, subset = Longitude == 0)
Rest_temp1 <- geocode_OSM(Rest_temp$City, as.sf = T)
Rest_temp1 <- as.data.frame(Rest_temp1)
Rest_temp1 <- Rest_temp1[,1:3]
colnames(Rest_temp1) <- c("City", "Latitude", "Longitude")
Rest_temp1 <- Rest_temp1[c(1,3,2)]
Rest_temp2 <- cbind(Rest_temp, Rest_temp1, by = "City")
Rest_temp2 <- Rest_temp2[c(1:7,21,22, 8:20, 23)]
Rest_temp2 <- Rest_temp2[, -c(10,11,22,23)]

RestDF <- RestDF[-which(RestDF$Longitude == 0),]
RestDF <- rbind(RestDF, Rest_temp2)
```

## Performing EDA:

## 1. Explore the geographical distribution of the restaurants and identify the 
## cities with the maximum and minimum number of restaurants  

Merging the two data sets
```{r}
RestDF1 <- merge(RestDF, Cntry_code, by = "Country Code")
head(RestDF1)
```

```{r}
count(RestDF1, Country, sort = T)
```

```{r}
ggplot(RestDF1,
       aes(x = Country)) +
  geom_bar(aes(x =  fct_infreq(Country), fill = Country),
           position = "dodge",
           stat = "count") +
  labs(title = "No of restaurants in each country",
       x = "Countries",
       y = "No. of restaurants") +
  theme(axis.text.x = element_text(angle = 75, size = 8),
        plot.title = element_text(hjust = 0.5))
```

India has the most number of restaurants - 8651, followed by USA - 434
The least number of restaurants are in Canada - 4

```{r}
count(RestDF1, Country, City, sort = T) %>% top_n(5, wt = n)
```

New Delhi has the most restaurants - 5473

```{r}
count(RestDF1, Country, City, sort = T) %>% top_n(-46, wt = n)
```

There are 46 cities in 7 countries that have only 1 restaurant


## 2. Restaurant franchising is a thriving venture. So, it is very important to
## explore the franchise with most national presence
```{r}
count(RestDF1, Country, `Restaurant Name`, sort = T) %>% top_n(10, wt = n)
```

Most franchises are in India. The biggest franchise in term of location is
Cafe Coffee Day with 83 restaurants   


Checking for franchises in the rest of the countries from the data set  
```{r}
RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Australia")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Brazil")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Canada")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Indonesia")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "New Zealand")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Phillipines")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Qatar")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Singapore")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "South Africa")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Sri Lanka")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Turkey")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "UAE")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "United Kingdom")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)

RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "United States")) %>%
  count(`Restaurant Name`, sort = T) %>%
  top_n(10, wt = n)
```

After India, the US has the most number of franchises - 4, followed by
Indonesia, UAE and UK with 3 franchises each


## 3. Find out the ratio between restaurants that allow table booking vs. those
## that do not allow table booking
```{r}
RestDF1$`Has Table booking` <-
  as.factor(RestDF1$`Has Table booking`)

Tbl_bkg <- ddply(
  RestDF1,
  ~ `Has Table booking`,
  summarize,
  No = sum(`Has Table booking` == "No"),
  Yes = sum(`Has Table booking` == "Yes")
)
Tbl_bkg$`Table booking` <- Tbl_bkg$No + Tbl_bkg$Yes
Tbl_bkg

(1158 / 9550) * 100
```

Only 12.1 % of the restaurants have the option to book a table

```{r message=FALSE, warning=FALSE}
plot_ly(
  Tbl_bkg,
  labels = ~ `Has Table booking`,
  values = ~ `Table booking`,
  type = 'pie',
  texttemplate = "%{label}: %{value:,} <br>(%{percent})"
) %>%
  layout(
    title = "Table Booking vs No Table Booking",
    legend = list(title = list(text = '<b> Table booking </b>')),
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
```

We can observe in the above pie chart that 87.9% of restaurants don't have a
table booking option  


## 4. Find out the percentage of restaurants providing online delivery

```{r}
RestDF1$`Has Online delivery` <-
  as.factor(RestDF1$`Has Online delivery`)

Online_bkg <- ddply(
  RestDF1,
  ~ `Has Online delivery`,
  summarize,
  No = sum(`Has Online delivery` == "No"),
  Yes = sum(`Has Online delivery` == "Yes")
)
Online_bkg$Online <- Online_bkg$No + Online_bkg$Yes
Online_bkg

(2451 / 9550) * 100
```

25.7 % of the restaurants provide online delivery

```{r}
plot_ly(
  Online_bkg,
  labels = ~ `Has Online delivery`,
  values = ~ Online ,
  type = 'pie',
  texttemplate = "%{label}: %{value:,} <br>(%{percent})"
) %>%
  layout(
    title = "Online Delivery vs No Online Delivery",
    legend = list(title = list(text = '<b> Online Delivery </b>')),
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
```

We can observe in the above pie chart that 74.3% of restaurants don't have an
online delivery service


## 5. Calculate the difference in number of votes for the restaurants that 
## deliver and the restaurants that do not deliver

```{r}
Vote <- RestDF1 %>%
  group_by(`Has Online delivery`) %>%
  summarise(Votes = sum(Votes))

Vote

sum(RestDF1$Votes)

979962 - 517915
```

Restaurants with Online delivery have 517915 Votes  
Restaurants without Online delivery have 979962 votes  
The difference in number of votes is 462047 in favor for the restaurants
without online delivery  

```{r}
Vote <- as.data.frame(Vote)

plot_ly(
  Vote,
  labels = ~ `Has Online delivery`,
  values = ~ Votes ,
  type = 'pie',
  texttemplate = "%{label}: %{value:,} <br>(%{percent})"
) %>%
  layout(
    title = "Votes - Online Delivery vs No Online Delivery",
    legend = list(title = list(text = '<b> Online Delivery </b>')),
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    )
  )
```

Restaurants without delivery have 65.4% out of the total votes and restaurants
that have delivery have only 34.6% of total votes.  
we conclude that other factors are more important in according higher votes.  


## 6. What are the top 10 cuisines served across cities?  
```{r}
Cuisine <-
  select(RestDF1, Country, City, `Restaurant Name`, Cuisines)

Ungrouped <- Cuisine %>%
  select(Cuisines, `Restaurant Name`) %>%
  separate_rows(Cuisines, sep = ", ") %>%
  count(`Restaurant Name`, Cuisines)

Cuisine1 <- merge(Cuisine, Ungrouped, by = "Restaurant Name")


Top10_City <- count(Cuisine1, City, Cuisines.y, sort = T) %>%
  top_n(10, wt = n)

ggplot(Top10_City,
       aes(x = Cuisines.y, y = n)) +
  geom_bar(stat = "identity", aes(fill = as.factor(City))) +
  labs(title = "Top 10 Cuisines Served",
       x = "Type of Cuisines",
       y = "No. of Cuisines",
       fill = "City") +
  scale_fill_brewer(palette = "Set2") +
  theme(plot.title = element_text(hjust = 0.5))
```

As we can observe from the above output in the top 10 cuisines served we have
only 3 cities: New Delhi, Noida and Gurgaon.  
We can also see that "North Indian" cuisine is the most served.  


Here are the top 10 cuisines in all of the countries
```{r message=FALSE, warning=FALSE}
set.seed(1)
wordcloud(
  words = RestDF1$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

Below are the top 10 cuisine per country

### Australia
```{r message=FALSE, warning=FALSE}
Australia <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Australia")) %>%
  count(Cuisines, sort = T)
set.seed(2)
wordcloud(
  words = Australia$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Brazil  
```{r message=FALSE, warning=FALSE}
Brazil <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Brazil")) %>%
  count(Cuisines, sort = T)
set.seed(3)
wordcloud(
  words = Brazil$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Canada
```{r message=FALSE, warning=FALSE}
Canada <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Canada")) %>%
  count(Cuisines, sort = T)
set.seed(4)
wordcloud(
  words = Canada$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### India
```{r message=FALSE, warning=FALSE}
India <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "India")) %>%
  count(Cuisines, sort = T)
set.seed(5)
wordcloud(
  words = India$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Indonesia
```{r message=FALSE, warning=FALSE}
Indonesia <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Indonesia")) %>%
  count(Cuisines, sort = T)
set.seed(6)
wordcloud(
  words = Indonesia$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### New Zealand
```{r message=FALSE, warning=FALSE}
New_Zealand <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "New Zealand")) %>%
  count(Cuisines, sort = T)
set.seed(7)
wordcloud(
  words = New_Zealand$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Phillipines
```{r message=FALSE, warning=FALSE}
Phillipines <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Phillipines")) %>%
  count(Cuisines, sort = T)
set.seed(8)
wordcloud(
  words = Phillipines$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Qatar
```{r message=FALSE, warning=FALSE}
Qatar <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Qatar")) %>%
  count(Cuisines, sort = T)
set.seed(9)
wordcloud(
  words = Qatar$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Singapore
```{r message=FALSE, warning=FALSE}
Singapore <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Singapore")) %>%
  count(Cuisines, sort = T)
set.seed(10)
wordcloud(
  words = Singapore$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### South Africa
```{r message=FALSE, warning=FALSE}
South_Africa <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "South Africa")) %>%
  count(Cuisines, sort = T)
set.seed(11)
wordcloud(
  words = South_Africa$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Sri Lanka
```{r message=FALSE, warning=FALSE}
Sri_Lanka <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Sri Lanka")) %>%
  count(Cuisines, sort = T)
set.seed(12)
wordcloud(
  words = Sri_Lanka$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### Turkey
```{r message=FALSE, warning=FALSE}
Turkey <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "Turkey")) %>%
  count(Cuisines, sort = T)
set.seed(13)
wordcloud(
  words = Turkey$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### UAE
```{r message=FALSE, warning=FALSE}
UAE <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "UAE")) %>%
  count(Cuisines, sort = T)
set.seed(14)
wordcloud(
  words = UAE$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### UK
```{r message=FALSE, warning=FALSE}
UK <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "United Kingdom")) %>%
  count(Cuisines, sort = T)
set.seed(15)
wordcloud(
  words = UK$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

### United States
```{r message=FALSE, warning=FALSE}
US <- RestDF1 %>%
  group_by(Country) %>%
  filter(any(Country == "United States")) %>%
  count(Cuisines, sort = T)
set.seed(16)
wordcloud(
  words = US$Cuisines,
  min.freq = 1,
  max.words = 10,
  random.order = FALSE,
  rot.per = 0.35,
  colors = brewer.pal(8, "Set2")
)
```

## 7. What is the maximum and minimum number of cuisines that a restaurant serves?
## Also, which is the most served cuisine across the restaurant for each city?

```{r}
count(Cuisine1, `Restaurant Name`, Cuisines.y, sort = T) %>%
  top_n(10, wt = n)

max(Cuisine1$n)
```

The maximum number of cuisines served by a restaurant is 83: Cuisine is Cafe and
the franchise name is Cafe Coffee Day  

```{r}
min(Cuisine1$n)
```

There are multiple restaurants that serve only one cuisine.  


## 8. What is the distribution cost across the restaurants?  
```{r message=FALSE, warning=FALSE}
qplot(
  RestDF1$`Average Cost for two`,
  geom = "histogram",
  binwidth = 30,
  main = "Histogram for Average Cost for two",
  xlab = "Avg Cost",
  fill = I("red"),
  col = I("blue"),
  alpha = I(.2)
)


qplot(
  RestDF1$`Average Cost for two`,
  geom = "histogram",
  binwidth = 30,
  main = "Histogram for Average Cost for two",
  xlab = "Avg Cost",
  fill = I("red"),
  col = I("blue"),
  alpha = I(.2),
  xlim = c(50, 1000)
)
```

From the above histograms we can observe that mostly the costs are between
250 and 550


## 9. How ratings are distributed among the various factors?  
## 10.Explain the factors in the data that may have an effect on ratings.  
## For example, number of cuisines, cost, delivery option, etc.  

```{r message=FALSE, warning=FALSE}
ggplot(RestDF1, aes(x = `Rating text`, fill = `Has Table booking`)) +
  geom_histogram(alpha = 0.5,
                 position = "dodge",
                 stat = "count")

ggplot(RestDF1, aes(x = `Rating text`, fill = `Has Online delivery`)) +
  geom_histogram(alpha = 0.5,
                 position = "dodge",
                 stat = "count")

```

Price Count & Rating Distribution
```{r}
RestDF1$`Average Cost for two Grp` <-
  cut(
    RestDF1$`Average Cost for two`,
    c(0, 200, 500, 1000, 3000, 5000, 10000, 800000),
    labels = c(
      "<=200",
      "<=500",
      "<=1000",
      "<=3000",
      "<=5000",
      "<=10000",
      "<=800000"
    )
  )

RestDF1 %>%
  filter(!is.na(`Average Cost for two Grp`)) %>%
  ggplot() +
  geom_bar(aes(x = `Average Cost for two Grp`, fill = `Average Cost for two Grp`),
           stat = "count") +
  labs(title = "Average Price") +
  theme(plot.title = element_text(hjust = 0.5))


RestDF1 %>%
  filter(!is.na(`Average Cost for two Grp`)) %>%
  ggplot() +
  geom_boxplot(aes(x = `Average Cost for two Grp`, y = `Aggregate rating`,
                   fill = `Average Cost for two Grp`)) +
  theme(plot.title = element_text(hjust = 0.5))

RestDF1 %>%
  ggplot() +
  geom_bar(aes(x = `Price range`, fill = as.factor(`Price range`)),
           stat = "count") +
  labs(title = "Price Range") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "Price range")

RestDF1 %>%
  ggplot() +
  geom_boxplot(aes(
    x = as.factor(`Price range`),
    y = `Aggregate rating`,
    fill = as.factor(`Price range`)
  )) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "Price range") +
  xlab("Price range")

RestDF1 %>%
  ggplot() +
  geom_point(aes(x = Votes, y = `Aggregate rating`))

RestDF1 %>%
  ggplot() +
  geom_boxplot(aes(
    x = `Has Table booking`,
    y = `Aggregate rating`,
    fill = as.factor(`Has Table booking`)
  )) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "Table booking") +
  xlab("Has table booking")

RestDF1 %>%
  ggplot() +
  geom_boxplot(aes(
    x = `Has Online delivery`,
    y = `Aggregate rating`,
    fill = as.factor(`Has Online delivery`)
  )) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "Online delivery") +
  xlab("Has online delivery")
```

We can observe that there is no single variable that affects the rating in a 
strong way however average cost for two, price range, number of votes, table
booking and online delivery are affecting in part the rating of a restaurant.
