---
title: "Healthcare cost analysis"
author: "Andrei Enescu"
date: "11/2/2020"
output: pdf_document
---

# DESCRIPTION  

# Background and Objective:  
   
   A nationwide survey of hospital costs conducted by the US Agency for
 Healthcare consists of hospital records of inpatient samples. The given data
 is restricted to the city of Wisconsin and relates to patients in the age
 group 0-17 years. The agency wants to analyze the data to research on
 healthcare costs and their utilization.  
 
# Domain: Healthcare  
 
# Dataset Description:  
   
Here is a detailed description of the given dataset:  
   
Attribute             Description  
**Age** 	            Age of the patient discharged  
**Female** 	          A binary variable that indicates if the patient is female  
**Los**	              Length of stay in days  
**Race** 	            Race of the patient (specified numerically)  
**Totchg**	          Hospital discharge costs  
**Aprdrg**	          All Patient Refined Diagnosis Related Groups  

# Analysis to be done:   
   
1. To record the patient statistics, the agency wants to find the age
category of people who frequently visit the hospital and has the maximum
expenditure.  

2. In order of severity of the diagnosis and treatments and to find out the
expensive treatments, the agency wants to find the diagnosis-related group
that has maximum hospitalization and expenditure.  
 
3. To make sure that there is no malpractice, the agency needs to analyze if
the race of the patient is related to the hospitalization costs.  

4. To properly utilize the costs, the agency has to analyze the severity of
the hospital costs by age and gender for the proper allocation of resources.  

5. Since the length of stay is the crucial factor for inpatients, the agency
wants to find if the length of stay can be predicted from age, gender, and 
race.  
 
6. To perform a complete analysis, the agency wants to find the variable that
mainly affects hospital costs.  

*****

These are the libraries I used:  

```{r message=FALSE, warning=FALSE}
library(rio)
library(dplyr)
```

Importing the data using RIO package  
```{r}
HospitalDF <- import("1555054100_hospitalcosts.xlsx")
```

Checking the data  
```{r}
head(HospitalDF)
str(HospitalDF)
summary(HospitalDF)
```

Changing Age, Female, Race variables into factors  
```{r}
HospitalDF$AGE <- as.factor(HospitalDF$AGE)
HospitalDF$FEMALE <- as.factor(HospitalDF$FEMALE)
HospitalDF$RACE <- as.factor(HospitalDF$RACE)
HospitalDF$APRDRG <- as.factor(HospitalDF$APRDRG)

str(HospitalDF)
```

## 1. To record the patient statistics, the agency wants to find the age
## category of people who frequently visit the hospital and has the maximum
## expenditure.

```{r}
summary(HospitalDF$AGE)
```

### Comments:  

Infants under 1 year group has the most hospital visits - **307**
```{r}
HospitalDF %>%
  group_by(AGE) %>%
  summarise(Expenditure = sum(TOTCHG)) %>%
  arrange(desc(Expenditure))
```

### Comments:  

Infants under 1 year group has the most hospital costs - **678118**
Based on the above outputs we can conclude that hospital costs are directly
proportional to hospital visits.  


## 2. In order of severity of the diagnosis and treatments and to find out the
## expensive treatments, the agency wants to find the diagnosis-related group
## that has maximum hospitalization and expenditure.

```{r}
count(HospitalDF, APRDRG, sort = T)

HospitalDF %>%
  group_by(APRDRG) %>%
  summarise(Expenditure = sum(TOTCHG)) %>%
  arrange(desc(Expenditure))
```

### Comments:  

Diagnosis-related group 640 has the most hospitalizations - **267** out of 
**500** - and the highest expenditure - **437978**


## 3. To make sure that there is no malpractice, the agency needs to analyze if
## the race of the patient is related to the hospitalization costs.

Removing NA value  
```{r}
HospitalDF <- na.omit(HospitalDF)
```

Using ANOVA  
```{r}
fit1 <- aov(HospitalDF$TOTCHG ~ HospitalDF$RACE)
summary(fit1)
summary(HospitalDF$RACE)
```

### Comments:  

As the p-value is higher than the significance level 0.05, we can conclude
that there are no significant differences between the groups in the model
summary. So by accepting the Null hypothesis we can say that there is no
relationship between race and hospitalization costs.  
Furthermore we can observe that we don't have a normal distributed data for
Race, where in group 1 we have 484 patients out of 500. we can conclude that
we don't have enough information to say if tha race is affecting the costs.


## 4. To properly utilize the costs, the agency has to analyze the severity of
## the hospital costs by age and gender for the proper allocation of resources.

```{r}
fit2 <- glm(TOTCHG ~ AGE + FEMALE, family = gaussian(), HospitalDF)
summary(fit2)
summary(HospitalDF$FEMALE)
```

### Comments:  

From above analysis we can conclude that the costs are not affected by gender,
but are significant affected by age.


## 5. Since the length of stay is the crucial factor for inpatients, the agency
## wants to find if the length of stay can be predicted from age, gender, and 
## race.

```{r}
fit3 <- glm(LOS ~ AGE + FEMALE + RACE, family = gaussian(), HospitalDF)
summary(fit3)
```

### Comments:  

The p-values for all independent variables are high, so we can say that there
is no relationship between the variables. We can conclude that based on the
given data we can not predict the length of stay based on age, gender or race.  


## 6. To perform a complete analysis, the agency wants to find the variable that
## mainly affects hospital costs.  

```{r}
fit4 <- lm(TOTCHG ~ ., HospitalDF)
summary(fit4)
```

### Comments:  

Based on the above analysis we concluded that Total Charge is highly affected
by: age,length of stay and , Diagnosis-related groups.  
Gender is moderately affecting the Total Charge.  
Race has no impact on Total Charge  
