---
title: "High value customers identification for an E-Commerce company"
author: "Andrei Enescu"
date: "11/2/2020"
output: pdf_document
---

# DESCRIPTION  

# Background of Problem Statement:  
   A UK-based online retail store has captured the sales data for different
 products for the period of one year (Nov 2016 to Dec 2017). The organization
 sells gifts primarily on the online platform. The customers who make a
 purchase consume directly for themselves. There are small businesses that buy
 in bulk and sell to other customers through the retail outlet channel.  

# Project Objective:  
   Find significant customers for the business who make high purchases of their
 favourite products. The organization wants to roll out a loyalty program to
 the high-value customers after identification of segments. Use the clustering
 methodology to segment customers into groups:  
  
# Domain: E-commerce  
 
# Dataset Description:  
   This is a transnational dataset that contains all the transactions occurring
 between Nov-2016 to Dec-2017 for a UK-based online retail store.  


**Attribute**	     Description  
**InvoiceNo**	     Invoice number (A 6-digit integral number uniquely assigned 
                   to each transaction)  
**StockCode**	     Product (item) code  
**Description** 	 Product (item) name  
**Quantity** 	     The quantities of each product (item) per transaction  
**InvoiceDate**	   The day when each transaction was generated  
**UnitPrice**	     Unit price (Product price per unit)  
**CustomerID**	   Customer number (Unique ID assigned to each customer)  
**Country**	       Country name (The name of the country where each customer 
                   resides)  

# Analysis tasks to be performed:     
1.   Use the clustering methodology to segment customers into groups:
    Use the following clustering algorithms:  
  
  1.1   K means  
  1.2   Hierarchical  

2. Identify the right number of customer segments.  
3. Provide the number of customers who are highly valued.  
4. Identify the clustering algorithm that gives maximum accuracy and explains 
   robust clusters.  
5. If the number of observations is loaded in one of the clusters, break down
   that cluster further using the clustering algorithm. [ hint: Here loaded
   means if any cluster has more number of data points as compared to other
   clusters then split that clusters by increasing the number of clusters and
   observe, compare the results with previous results.]   

*****

These are the libraries I used:  
```{r message=FALSE, warning=FALSE}
library(rio)
library(DataExplorer)
library(ggplot2)
library(factoextra)
library(NbClust)
```

Importing the data using RIO package  
```{r}
EcommDF <- import("Ecommerce.csv")
```

Checking the data structure  
```{r}
head(EcommDF)
summary(EcommDF)
str(EcommDF)
```

Removing empty column  
```{r}
EcommDF <- EcommDF[, 1:8]
```

Checking and removing NA values  
```{r}
options(scipen = 999)
plot_missing(EcommDF, title = "Missing values in every column")

EcommDF <- na.omit(EcommDF)
```

Leaving only unique customers  
```{r}
EcommDF <- EcommDF[unique(EcommDF$CustomerID), ]
```

Remove Quantity with negative values  
```{r}
EcommDF <- EcommDF[EcommDF$Quantity >= 0,]
```

Add a "Total Spent" column   
```{r}
EcommDF$TotalSpent <- EcommDF$Quantity * EcommDF$UnitPrice
```

Variables should be numeric  
```{r}
EcommDF_Num <- EcommDF[, -c(3, 5, 8)]
str(EcommDF_Num)

EcommDF_Num$InvoiceNo <- as.numeric(EcommDF_Num$InvoiceNo)
EcommDF_Num$StockCode <- as.numeric(EcommDF_Num$StockCode)
EcommDF_Num$Quantity <- as.numeric(EcommDF_Num$Quantity)
EcommDF_Num$CustomerID <- as.numeric(EcommDF_Num$CustomerID)

summary(EcommDF_Num)
```

Outlier removal  
```{r}
Quantity_LT <- mean(EcommDF_Num$Quantity) - 2 * sd(EcommDF_Num$Quantity)
Quantity_UT <- mean(EcommDF_Num$Quantity) + 2 * sd(EcommDF_Num$Quantity)

UnitPrice_LT <- mean(EcommDF_Num$UnitPrice) - 2 * sd(EcommDF_Num$UnitPrice)
UnitPrice_UT <- mean(EcommDF_Num$UnitPrice) + 2 * sd(EcommDF_Num$UnitPrice)
```

Threshold  
```{r}
EcommDF_Num$Quantity <-
  ifelse(EcommDF_Num$Quantity > Quantity_UT, Quantity_UT, EcommDF_Num$Quantity)
EcommDF_Num$Quantity <-
  ifelse(EcommDF_Num$Quantity < Quantity_LT, Quantity_LT, EcommDF_Num$Quantity)

EcommDF_Num$UnitPrice <-
  ifelse(EcommDF_Num$UnitPrice > UnitPrice_UT, UnitPrice_UT, EcommDF_Num$UnitPrice)
EcommDF_Num$UnitPrice <-
  ifelse(EcommDF_Num$UnitPrice < UnitPrice_LT, UnitPrice_LT, EcommDF_Num$UnitPrice)
```

Remove scaling effect from data  
```{r}
EcommDF_Num <- scale(EcommDF_Num)
summary(EcommDF_Num)
```

Removing NA values  
```{r}
EcommDF_Num <- na.omit(EcommDF_Num)
```

## 1.   Use the clustering methodology to segment customers into groups:
    Use the following clustering algorithms:  
  
  ## 1.1 K means  

**Elbow method**  
```{r}
fviz_nbclust(EcommDF_Num, kmeans, method = "wss") +
  geom_vline(xintercept = 4, linetype = 2)+
  labs(subtitle = "Elbow method")
```

**Silhouette method**  
```{r}
fviz_nbclust(EcommDF_Num, kmeans, method = "silhouette")+
  labs(subtitle = "Silhouette method")
```

**Gap statistic**  
```{r}
set.seed(123)
fviz_nbclust(EcommDF_Num, kmeans, method = "gap_stat", nboot = 50)+
  labs(subtitle = "Gap statistic method")
```

### Comments: 

We can observe that these three methods do not necessarily lead to the same 
result. All 3 approaches suggest a different number of clusters.  

In this case we can use a 4th alternative - *NbClust* function, which provides
30 indices for choosing the best number of clusters.   
```{r}
NC <- NbClust(EcommDF_Num, distance = "euclidean",
        min.nc = 2, max.nc = 15, method = "kmeans")

barplot(table(NC$Best.n[1,]),
        xlab="Number of Clusters", ylab="Number of Criteria",
        main="Number of Clusters Chosen by Criteria")

KM_res <- kmeans(EcommDF_Num, centers = 2)
fviz_cluster(KM_res, EcommDF_Num, ellipse.type = "norm")

KM_res$centers
```

### Comments: 

Based on all 30 indices, the best number of clusters is 2 clusters.  
By looking at the centers of the two clusters we can observe that there is no 
overlapping.  


  ## 1.2 Hierarchical  

Calculate distances between observations  
```{r}
Dist.Ecomm <- dist(EcommDF_Num, method = 'euclidean')

HC <- hclust(Dist.Ecomm, method = "single")
plot(HC, hang = -1)
rect.hclust(HC, k = 2, border = 2:5)
```

## 2. Identify the right number of customer segments. 

According to the majority rule, the best number of clusters is  2 

## 3. Provide the number of customers who are highly valued.
```{r}
sum(EcommDF$TotalSpent > mean(EcommDF$TotalSpent))
```

The most valuable customers buy more or higher-value products than the average
customer. So we can conclude that there are *868* highly valued clients

## 4. Identify the clustering algorithm that gives maximum accuracy and explains
##    robust clusters.

  For the given dataset the maximum accuracy is obtained by using partitioning
method clustering, more exactly the K-means clustering
