---
title: "Insurance factors identification"
author: "Andrei Enescu"
date: "10/21/2020"
output: pdf_document
---

# Description

# Background and Objective:
  The data gives the details of third party motor insurance claims in Sweden
  for the year 1977. In Sweden, all motor insurance companies apply identical 
  risk arguments to classify customers, and thus their portfolios and their 
  claims statistics can be combined. The data were compiled by a Swedish 
  Committee on the Analysis of Risk Premium in Motor Insurance. The Committee 
  was asked to look into the problem of analyzing the real influence on the 
  claims of the risk arguments and to compare this structure with the actual
  tariff.

# Domain: Insurance

# Dataset Description: 
   The insurance dataset holds 7 variables and the description of these 
   variables are given below: 
  
#   Attribute	Description
  **Kilometers:**	Kilometers traveled per year   
                  1: < 1000  
                  2: 1000-15000   
                  3: 15000-20000   
                  4: 20000-25000   
                  5: > 25000  
  **Zone:**	      Geographical zone   
                  1: Stockholm, Göteborg, and Malmö with surroundings  
                  2: Other large cities with surroundings   
                  3: Smaller cities with surroundings in southern Sweden   
                  4: Rural areas in southern Sweden   
                  5: Smaller cities with surroundings in northern Sweden   
                  6: Rural areas in northern Sweden  
                  7: Gotland  
  **Bonus:**      No claims bonus; equal to the number of years, plus one, since  
                  the last claim.  
  **Make:**	      1-8 represents eight different common car models. All other 
                  models are combined in class 9.  
  **Insured:** 	  The number of insured in policy-years.  
  **Claims:**	    Number of claims  
  **Payment:** 	  The total value of payments in Skr (Swedish Krona)  

# Analysis Tasks: 
  After understanding the data, you need to help the committee with the 
following by the use of the R tool:

1. The committee is interested to know each field of the data collected through
descriptive analysis to gain basic insights into the data set and to prepare
for further analysis.    
2. The total value of payment by an insurance company is an important factor to
be monitored. So the committee has decided to find whether this payment is
related to the number of claims and the number of insured policy years. They
also want to visualize the results for better understanding.   
3. The committee wants to figure out the reasons for insurance payment increase
and decrease. So they have decided to find whether distance, location, bonus,
make, and insured amount or claims are affecting the payment or all or some of
these are affecting it.    
4. The insurance company is planning to establish a new branch office, so they
are interested to find at what location, kilometer, and bonus level their
insured amount, claims, and payment gets increased. (Hint: Aggregate Dataset)   
5. The committee wants to understand what affects their claim rates so as to
decide the right premiums for a certain set of situations. Hence, they need to
find whether the insured amount, zone, kilometer, bonus, or make affects the
claim rates and to what extent.   
*****

Used libraries:    
```{r}
library(rio)
library(ggplot2)
```

Importing the data using RIO package  
```{r}
InsuranceDF <- import("Insurance_factor_identification.csv")
```

Checking data  
```{r}
head(InsuranceDF)
str(InsuranceDF)
which(is.na(InsuranceDF))
```

## 1. The committee is interested to know each field of the data collected
## through descriptive analysis to gain basic insights into the data set and
## to prepare for further analysis.    
```{r}
str(InsuranceDF)
summary(InsuranceDF)
```

### Observation  

On the output we have a sumary of each column from the dataset.  

## 2. The total value of payment by an insurance company is an important factor
## to be monitored. So the committee has decided to find whether this payment is
## related to the number of claims and the number of insured policy years. They
## also want to visualize the results for better understanding.     

Correlation between Payment & Claims  
```{r}
cor(InsuranceDF$Payment, InsuranceDF$Claims)
ggplot(InsuranceDF,
       aes(x = Claims, y = Payment, label = Payment)) +
  geom_point(size = 1.5) +
  labs(title = "Correlation between Payment & Claims",
       x = "Claims",
       y = "Payment") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(labels = scales::comma)
```

Correlation between Payment & No of insured policy years  
```{r}
cor(InsuranceDF$Payment, InsuranceDF$Insured)
ggplot(InsuranceDF,
       aes(x = Insured, y = Payment, label = Payment)) +
  geom_point(size = 1.5) +
  labs(title = "Correlation between Payment & Insured policy years",
       x = "Insured Policy Years",
       y = "Payment") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(labels = scales::comma)
```

### Observation  

From the correlation output we can observe that there is a strong positive
correlation between Payment and Claims (99.5%) and also between Payment and
Insured policy years (93.3%)  
From both plots we observe that as Claims or Insured policy years increase, the
Payment increases also  


## 3. The committee wants to figure out the reasons for insurance payment
## increase and decrease. So they have decided to find whether distance, 
## location, bonus, make, and insured amount or claims are affecting the payment
## or all or some of these are affecting it.   

```{r}
fit1 <- lm(Payment ~ ., InsuranceDF)
summary(fit1)
```

### Observation  

From the output we conclude the following:  
  * Kilometers, Zone, Insured and Claims are all significant variables and are
  affecting the Payment  
  * Make and Bonus, both have a higher P-value so they are affecting Payment in
  a lower manner  
  

## 4. The insurance company is planning to establish a new branch office, so
## they are interested to find at what location, kilometer, and bonus level
## their insured amount, claims, and payment gets increased.  

```{r}
Zone <-
  apply(InsuranceDF[, c(5, 6, 7)], 2, function(x)
    tapply(x, InsuranceDF$Zone, mean))
Zone

KM <-
  apply(InsuranceDF[, c(5, 6, 7)], 2, function(x)
    tapply(x, InsuranceDF$Kilometres, mean))
KM

Bonus <-
  apply(InsuranceDF[, c(5, 6, 7)], 2, function(x)
    tapply(x, InsuranceDF$Bonus, mean))
Bonus
```

### Observation  

From the above outputs we can conclude:  
  * Zone 4 has the highest Claims and Payment  
  * Zone 7 has the lowest Insured, Claims and Payment  
  * Kilometer group 2 has the highest Claims and Payment  
  * Kilometer group 5 has the lowest Claims and Payment  
  * Bonus group 7 has the highest Insured, Claims and Payment  

So for a new branch office, in order to have an increase in Payment they need to
select Zone 4, Kilometers traveled per year: 1000 - 15000 (group 2) and seven
years as Bonus


## 5. The committee wants to understand what affects their claim rates so as to
## decide the right premiums for a certain set of situations. Hence, they need
## to find whether the insured amount, zone, kilometer, bonus, or make affects
## the claim rates and to what extent.   

```{r}
fit2 <- lm(Claims ~ ., InsuranceDF)
summary(fit2)
```

### Observation 

From the linear model we can conclude that all the independent variables have
a high significance on the Claim variable.

